\begin{thebibliography}{99}
%\begin{bibliography}{}
\addcontentsline{toc}{chapter}{参考文献}

% intro
\bibitem{11ubi}       Yu Zheng, Yanchi Liu, Jing Yuan, and Xing Xie, Urban Computing with Taxicabs, In Proc. of Ubicomp 2011, pp. 89--98, 2011.
\bibitem{surechigai}  末廣 創，佐藤 文明，すれ違い通信による情報伝搬モデルの特性評価，情報処理学会全国大会講演論文集 第72回(ネットワーク), 155-156, 2010-03-08, 2010.
\bibitem{clicker}     April R. Trees, and Michele H. Jackson. The learning environment in clicker classrooms: student processes of learning and involvement in large university‐level courses using student response systems. Learning, Media and Technology, vol.32, no.1, pp.21--40, 2007.
\bibitem{imakiku}     株式会社天問堂, Imakiku, \url{http://tenmondo.com/products/imakiku/index.html} (2015時点)
\bibitem{twitter}     後藤 真孝, WISS 2010 と WISS 2011 での改革, コンピュータソフトウェア (日本ソフトウェア科学会誌), Vol.29, No.4, pp.3--8, 2012.

% related
\bibitem{kawagoe14} 河越嵩介，神場知成，田中二郎．位置情報を利用した携帯端末への音声情報配信，情報処理学会第76回全国大会，4ZA-2，2014.
\bibitem{wfs}       Berkhout, Augustinus J., Diemer de Vries, and Peter Vogel. "Acoustic control by wave field synthesis." The Journal of the Acoustical Society of America 93.5 (1993): 2764-2778.
\bibitem{hoa}       Daniel, Jérôme. "Spatial sound encoding including near field effect: Introducing distance coding filters and a viable, new ambisonic format." Audio Engineering Society Conference: 23rd International Conference: Signal Processing in Audio Recording and Reproduction. Audio Engineering Society, 2003.
\bibitem{sfc}       Ise, Shiro. "A principle of sound field control based on the Kirchhoff-Helmholtz integral equation and the theory of inverse systems." Acta Acustica united with Acustica 85.1 (1999): 78-87.
\bibitem{paramsp}   青木茂明，清水一博，伊藤昂輝．パラメトリックスピーカを用いた再生時の音像定位．信学技報 EA研究会，vol.114，no.423, pp.33--38, 2015.
\bibitem{shibata13} 柴田一暁, 小野順貴, 亀岡弘和. 音の発信を利用したスマートフォンアレイの機器位置推定. 音講論 (秋), pp.591--592, 2013.
\bibitem{shibata14} 柴田一暁, 小野順貴, 亀岡弘和. 音の発信を利用したキャリブレーションに基づくアドホックマイクロホンアレイによる音源定位. 音講論 （春）, pp. 707--710，2014.
\bibitem{Aoshima}   N. Aoshima, Computer-generated pulse signal applied for sound measurement, J. Acoust. Soc. Am., vol.69, no.5,1484--1488, 1981.


% system
\bibitem{dbap}      Trond Lossius, Pascal Baltazar, and Theo de la Hogue. DBAP–distance-based amplitude panning. Proc of ICMC 2009, pp.489--492, 2009.
\bibitem{tpsn}      Ganeriwal, Saurabh, Ram Kumar, and Mani B. Srivastava. "Timing-sync protocol for sensor networks." Proceedings of the 1st international conference on Embedded networked sensor systems. ACM, 2003.
\bibitem{Haas}      (After Helmut Haas's doctorate dissertation presented to the University of Gottingen, Gottingen, Germany as "Über den Einfluss eines Einfachechos auf die Hörsamkeit von Sprache;" translated into English by Dr. Ing. K.P.R. Ehrenberg, Building Research Station, Watford, Herts., England Library Communication no. 363, December, 1949; reproduced in the United States as "The Influence of a Single Echo on the Audibility of Speech," J. Audio Eng. Soc., Vol. 20 (Mar. 1972), pp. 145-159.)
\bibitem{pof}       Horner, Joseph L., and Peter D. Gianino. "Phase-only matched filtering." Applied optics 23.6 (1984): 812-816.
\bibitem{overwrap}  Rabiner, Lawrence R., and Bernard Gold. "Theory and application of digital signal processing." Englewood Cliffs, NJ, Prentice-Hall, Inc., 1975. 777 p. 1 (1975).

\bibitem{umezu11}   梅津直貴, 井ノ上寛人, 堀内恒, 佐藤美恵, 小黒久史, 春日正男.空間把握性に注目した音響案内システムの開発に関する研究.映像情報メディア学会技術報告 vol.35, no.39, pp.41--44,2011.
\bibitem{onzou}     平原達也, 蘆原郁, 小澤賢司, 宮坂榮一, 音と人間, 日本音響学会編, コロナ社, 2013.


\bibitem{raylei1877}
Lord Rayleigh, Acoustical Observations I,
Philosophical Magazine Series 5, vol. 3, Issue 20, pp.456--464, 1877.
%http://www.tandfonline.com/doi/abs/10.1080/14786447708639268?journalCode=tphm16
\bibitem{raylei1907}
Lord Rayleigh, On our perception of sound direction,
Philosophical Magazine Series 6, vol. 13, Issue 74, pp.214--232, 1907.
%http://www.tandfonline.com/doi/abs/10.1080/14786440709463595#abstract
%[Lord Rayleigh: On our perception of sound direction, Phil.Mag, 13,6th series,pp.214-232(1907)]
\bibitem{komatsu2014}
小松潤也, 塩田茂雄, センサ協調位置推定: 相互多辺測量法と多次元尺度構成法の精度比較, 信学技報, ASN 114(65), pp.127--132, 2014.
\bibitem{senkouon}
H. Haas, The Influence of a Single Echo on the Audibility of Speech,
Journal of Auditory Engineering Society, vol. 20, Issue 2, pp.146--159, 1972.
%http://www.aes.org/e-lib/browse.cfm?elib=2093
%播摩敏雄, 安倍幸治, 高根昭一, 曽根敏夫, 音像定位における先行音効果とエコー知覚の限界に関する考察, HIP 104(526), pp.13--18, 2004.
%http://ci.nii.ac.jp/els/110003272588.pdf?id=ART0003775596&type=pdf&lang=jp&host=cinii&order_no=&ppv_type=0&lang_sw=&no=1451791039&cp=
\bibitem{vbap}
Vikke Pulkki, Virtual Sound Source Positioning Using Vector Base Amplitude Panning, Journal of Audio Engineering Society, Vol. 45, Issue 6, pp.456--466, 1997.

%Trond Lossius, et al., DBAP - Distance based amplitude panning, International ComputerMusic Conference (ICMC). Montreal, 2009.
\bibitem{self_ac}
伊納洋祐, 吉田侑矢, 米澤朋子,	複数端末の音響的位置推定と同期による空間音響環境構築システムの提案,	ASJ 2014 autumn,	pp.1439--1440,	2014.
\bibitem{seigoufilter}
滑川俊彦，奥井重彦，衣斐信介，通信方式(第二版)，森北出版，2012.
\bibitem{pulsecompress}
近藤倫正，, 実森彰郎，大橋由昌，計測・センサにおけるディジタル信号処理，昭晃堂，1993．
\bibitem{chordalg}
I. Stoica, R. Morris, D. Karger, M. F. Kaashoek, H. Balakrishnan.
Chord: A scalable peer-to-peer lookup service for internet applications.
ACM SIGCOMM Computer Communication Revies, vol. 31, issue 4, pp.149--160,
2001.
\bibitem{morimoto95}
Morimoto, Masayuki, and Kazuhiro Iida. A practical evaluation method of auditory source width in concert halls. Journal of the Acoustical Society of Japan (E) vol.16, no.2, pp.59--69, 1995.
\bibitem{barron81}
M. Barron, and A. H. Marshall. Spatial impression due to early lateral reflections in concert halls: the derivation of a physical measure. Journal of Sound and Vibration, vol.77, no.2, pp.211--232, 1981.
%音響工学基礎論
\bibitem{suehiro06}
末廣大地, 翁長博, 池田哲朗. 音楽ホールにおける音に包まれた感じに対応する物理指標の検討. 日本建築学会環境系論文集，no.599, pp.1--7, 2006.
\bibitem{cheun97}
Kyungwhoon Cheun. Performance of Direct-Sequence Spread-Spectrum RAKE Receivers with Random Spreading Sequences.
IEEE Transactions on communications, vol.45, no.9, pp.1130--1143, 1997.
\bibitem{honer84}
J. L. Horner, P. D. Gianino. Phase-only matched filtering. Applied optics, vol.23, no.6, pp.812--816, 1984.
%C言語によるディジタル無線通信技術
%アコースティック・イメージング
%原理が分かる・現場で使える信号処理

%http://sonove.angry.jp/about_localization.html
%http://acousticslab.org/psychoacoustics/PMFiles/Module07b.htm

\end{thebibliography}
%\end{bibliography}{}
